\documentclass{article}

\usepackage[margin=1in]{geometry}

% \usepackage{hyperref}

\usepackage{cite}
\usepackage{url}
\usepackage{graphicx}
\usepackage{color}

\usepackage{graphicx}

\usepackage{amssymb,amsmath}

\usepackage{parskip}

\usepackage{algorithm}

\usepackage[noend]{algorithmic}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\newcommand{\fig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\Name}{\emph{Hidden Target}~}

\newcommand{\Acronym}[1]{\ensuremath{{{\texttt{#1}}}}}
\newcommand{\Symbol}[1]{\ensuremath{\mathcal{#1}}}
\newcommand{\Function}[1]{\ensuremath{{\textsc{#1}}}}
\newcommand{\Constant}[1]{\ensuremath{{\texttt{#1}}}}
\newcommand{\Var}[1]{\ensuremath{{{\textsl{#1}}}}}
\newcommand{\False}{\Constant{false}}
\newcommand{\True}{\Constant{true}}
\newcommand{\Null}{\Constant{null}}
\newcommand{\Revision}[1]{\textcolor{red}{#1}}
\newcommand{\R}{\ensuremath{\mathbb{R}}}
\newcommand{\Traj}{\ensuremath{\zeta}}
\newcommand{\Tree}{\Symbol{T}}
\newcommand{\pair}[1]{\ensuremath{\langle#1\rangle}}


\begin{document}

\setlength{\parskip}{4pt} % 1ex plus 0.5ex minus 0.2ex}

\title{Appeal for Financial Aid}

\author{Alexander J. Wallar \\ B.Sc in Computer Science, University of St Andrews, UK
\\ \url{http://aw204.host.cs.st-andrews.ac.uk}}

\maketitle

Whilst at university, I have been a student ambassador for STEM programs for schools around the Fife area. We would go to schools and science fairs in Fife and the surrounding area to teach kids how to program MindStorms robots to move around a structured environment with a drag and drop programming language. At the schools we would go through the instruction manual and teach the students how to put the robots together.

Since my junior year, I have participated in the mentoring scheme at my university. This meant taking a first year student under my supervision and make sure that they are understanding the material. Also, now during my final year, I have been tutoring a second year student focussing on algorithms, data structures, and internet programming.

I also provide assistance on university visiting days by giving tours of the school of computer science and answering questions from the prospective students.

Since I have started university, I have been participating in research. I have held internship placements and research assistantships throughout my university career. These positions have lead to three accepted conference publications and one submitted journal publication involving swarm robotics and motion planning. I am able to work independently to solve difficult tasks with little supervision. This is shown through my affiliation with the Catholic University of America which I have been employed whilst living in Scotland.

\bibliographystyle{ieeetr} \bibliography{proposal}

\end{document}
