\documentclass{article}

\usepackage[margin=1in]{geometry}

% \usepackage{hyperref}

\usepackage{cite}
\usepackage{url}
\usepackage{graphicx}
\usepackage{color}

\usepackage{graphicx}

\usepackage{amssymb,amsmath}

\usepackage{parskip}

\usepackage{algorithm}

\usepackage[noend]{algorithmic}

\renewcommand{\thefootnote}{\fnsymbol{footnote}}

\newcommand{\fig}[1]{Fig.~\ref{fig:#1}}
\newcommand{\Name}{\emph{Hidden Target}~}

\newcommand{\Acronym}[1]{\ensuremath{{{\texttt{#1}}}}}
\newcommand{\Symbol}[1]{\ensuremath{\mathcal{#1}}}
\newcommand{\Function}[1]{\ensuremath{{\textsc{#1}}}}
\newcommand{\Constant}[1]{\ensuremath{{\texttt{#1}}}}
\newcommand{\Var}[1]{\ensuremath{{{\textsl{#1}}}}}
\newcommand{\False}{\Constant{false}}
\newcommand{\True}{\Constant{true}}
\newcommand{\Null}{\Constant{null}}
\newcommand{\Revision}[1]{\textcolor{red}{#1}}
\newcommand{\R}{\ensuremath{\mathbb{R}}}
\newcommand{\Traj}{\ensuremath{\zeta}}
\newcommand{\Tree}{\Symbol{T}}
\newcommand{\pair}[1]{\ensuremath{\langle#1\rangle}}

\begin{document}

\setlength{\parskip}{4pt} % 1ex plus 0.5ex minus 0.2ex}

\title{Recommendation Letter for Alexander Wallar}

\author{Donald Sofge Ph.D.\\Naval Center for Applied Research in Artificial
Intelligence\\Naval Research Laboratory\\donald.sofge@nrl.navy.mil}

\maketitle

Dear Committee,

I am hereby providing a letter of recommendation to support his application of
Alexander Wallar for the Ph.D. program at your institution. I was his
supervisor during his summer internship at the Naval Center for Applied
Research in Artificial Intelligence at the Naval Research Laboratory during the
summer of 2014.

Alex is an outstanding student with full of drive and enthusiasm with a great
willingness to learn and to contribute to research. A Ph.D. will provide Alex
the opportunity to continue his research under the supervision of experts in
the field, further strengthening his ability to conduct high quality research
in computer science and robotics.

Alex applied for the Naval Enterprise Research Internship Program and I
accepted him to work for the Distributed Autonomous Systems Group that I lead
in the summer of 2014. Alex worked on a path planning algorithm that enables a
team of unmanned aerial vehicles to efficiently conduct surveillance of risk
sensitive areas. The algorithm he developed was able to survey a given area
whilst minimizing the risk of damage to the vehicle and maximize the quality of
the captured sensory information. Alex developed the algorithm in simulation
and on physical quadrotors (AscTec Pelicans) using the Robotic Operating System
(ROS). He also developed a middleware that extended ROS to seamlessly supports
multiple robots. The work Alex completed over the summer led to two paper
submissions, one conference paper that was accepted and a journal paper that is
currently under review. Alex will be working in my lab during January of 2015
has a student contractor.

The quality of research and work ethic Alex exhibited goes beyond the
expectations of a undergraduate summer intern and is what should expected from
a graduate student conducting research in robotics. This demonstrates Alex's
ability to solve challenging problems, to work independently, and to succeed in
a Ph.D. program.

In summary, I fully support Alex's application to pursue a Ph.D. at your
institution. Alex has exhibited his ability to conduct research in robotics and
to prepare this research for publication and acceptance in the research
community. The Ph.D. program will provide Alex with opportunities to continue
his research and prepare him for a career in academia. Please feel free to
contact me if any additional information is needed to support his application.
\\ \\Sincerely,

Donald Sofge

\end{document}
